MSHS COVID-19 Vaccination Summary

### 2022-09-15 MSHS Vaccines Administered Hybrid Data Model.Rmd
Add scripts used to create and render hybrid data model dashboard to repository.

# Determine whether or not to update an existing repo
update_repo <- FALSE

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

# Vaccine types
vax_types <- c("Adult (12 yo +)", "Peds (5-11 yo)", "Peds (6 mo - 4 yo)")

@@

```{r Import existing repo and append as needed}
# Import schedule repository daily summary for 2020 and 2021
sched_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Sched Arr Visits 2020-2021 Daily Summary 2022-08-12.RDS"))

# Import vaccine administration repository daily summary for Jan-Jun 2022
vax_admin_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-19.RDS"))

@@

# # Needs to be updated once we start receiving weekly reports
# if (update_repo) {
# 
#   # Determine date range of reports to add to repository
#   if (sched_repo_update_date == today - 1) {
#     new_report_dates <- today - 1
#   } else {
#     new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
#   }
# 
#   new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
# 
#   # Find list of reports
#   file_list_vacc_sched <- list.files(
#     path = paste0(user_directory,
#                   "/Epic Auto Report Sched All Status"),
#     pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
#                      new_report_dates_pattern,
#                      ".*.csv",
#                      collapse = "|"))
# 
#   # Import reports and add a column with report name and report date
#   import_new_reports <- map_df(
#     file_list_vacc_sched,
#     .f = function(x){
#       sched_data <- read.csv(
#         paste0(user_directory,
#                "/Epic Auto Report Sched All Status/",
#                x),
#         stringsAsFactors = FALSE,
#         check.names = FALSE) %>%
#         mutate(Filename = x,
#                ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
#                                     "%Y%m%d"),
#                DOB = as.Date(DOB, format = "%m/%d/%Y"),
#                `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
#                Date = as.Date(Date, "%m/%d/%Y"),
#                `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
#                                         tz = "", format = "%Y-%m-%d %H:%M %p"),
#                `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
#                `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
#                  `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
#     }
#   )
# 
#   # Filter schedule data from new reports to only keep appointments in latest reports
#   sched_data_new_reports <- import_new_reports %>%
#     group_by(Date) %>%
#     slice_max(ReportDate) %>%
#     mutate(Filename = NULL,
#            ReportDate = NULL) %>%
#     ungroup()
# 
#   new_reports_dates <- sort(unique(sched_data_new_reports$Date))
# 
#   # Remove vaccine appoints from any overlapping dates in repository and new reports
#   sched_repo <- sched_repo %>%
#     filter(!(Date >= new_reports_dates[1]))
# 
#   # Bind schedule repository and schedule from new reports
#   sched_repo <- rbind(sched_repo, sched_data_new_reports)
# 
#   # Save new repository
#   saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
#                              "Auto Epic Report Sched ",
#                              format(min(sched_repo$Date), "%m%d%y"), " to ",
#                              format(max(sched_repo$Date), "%m%d%y"),
#                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
# 
# } else {
# 
# }
```

```{r Format and process new immunization data}
# new_immune_data <- unique(data)
# 
# new_immune_data <- left_join(new_immune_data,
#                              vax_admin_data_mappings,
#                              by = c("EPICDEPID" = "EpicID"))
# 
# # Add in logic to check for unmapped departments that need to be added to mapping file
# # Note: This is different than immunizations without a department listed
# 
# new_immune_data <- new_immune_data %>%
#   select(-DOSE) %>%
#   mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
#                       ifelse(str_detect(IMMUNE_NAME, "MODERNA"), "Moderna",
#                              ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
#                                     NA))),
#          VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
#                           "Peds (5-11 yo)",
#                           ifelse(str_detect(IMMUNE_NAME,
#                                             "(\\(6 MONTHS - 4 YEARS\\))"),
#                                  "Peds (6 mo - 4 yo)", 
#                           "Adult (12 yo +)")),
#          Dose = ifelse(str_detect(replace_na(PRC_NAME, ""), "DOSE 1"),
#                        "Dose 1",
#                        ifelse(str_detect(replace_na(PRC_NAME, ""),
#                                          "DOSE 2"), "Dose 2",
#                               ifelse(str_detect(replace_na(PRC_NAME, ""),
#                                                 "(DOSE 3)|(BOOSTER)"),
#                                      "Dose 3/Booster", "Dose 3/Booster"
#                               ))),
#          Date = as.Date(str_extract(IMMUNE_DATE,
#                                     "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
#                         format = "%d-%b-%Y")
#          ) %>%
#   rename(Department = DEPARTMENT_NAME)
# 
# new_immune_data_daily_summary <- new_immune_data %>%
#   filter(!is.na(Department)) %>%
#   group_by(Date, Department, `Setting Grouper`, 
#            Site, `Hospital Roll Up`, 
#            VaxType, Dose, Mfg) %>%
#   summarize(Count = n()) %>%
#   ungroup()
# 
# # Add to existing summary
# hybrid_repo <- rbind(hybrid_repo,
#                      new_immune_data_daily_summary)

@@

setting_kable(setting = "Hospital POD",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (6 mo - 4 yo)")

@@

setting_kable(setting = "MSHS Practice",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (6 mo - 4 yo)")

@@

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Adult (12 yo +)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (5-11 yo)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (6 mo - 4 yo)")

@@

*   Immunizations with no associated Department/Epic ID excluded from analysis.
*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
*   Vaccine dose based on the following logic:
    1. PRC_NAME field in Epic for clearly defined visits.
    2. RESPONSE_LIST field completed during vaccination noting the dose in the series for ambiguously defined visits (ie, well visits, follow ups, etc.)

>>>>

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

# Vaccine types
vax_types <- c("Adult (12yo+)", "Peds (5-11yo)", "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")

@@

```{r Import existing repo and append as needed}
# Import schedule repository daily summary for 2020 and 2021
sched_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

# Import vaccine administration repository daily summary for Jan-Jun 2022
vax_admin_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-09-14.RDS"))

@@

# Needs to be updated once we start receiving weekly reports
if (update_repo) {

  # Select most recent weekly file
  weekly_vax_admin <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report/*.*"))

  weekly_vax_admin <- read.csv(weekly_vax_admin)

  weekly_vax_admin <- unique(weekly_vax_admin)

  weekly_vax_admin <- left_join(weekly_vax_admin,
                                vax_admin_data_mappings,
                                by = c("EPICDEPID" = "EpicID"))

  unmapped_dept <- weekly_vax_admin %>%
    select(DEPARTMENT_NAME, EPICDEPID, Site) %>%
    distinct() %>%
    filter(!is.na(DEPARTMENT_NAME) & is.na(Site))

  if(nrow(unmapped_dept) > 0) {
    stop(paste0("Check department mappings. Missing departments include ",
                paste(as.vector(unmapped_dept$DEPARTMENT_NAME), collapse = ", "),
                "."))
  }

  weekly_vax_admin <- weekly_vax_admin %>%
    select(-DOSE) %>%
    mutate(VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
                            "Peds (Pfizer 5-11yo)",
                            ifelse(str_detect(IMMUNE_NAME,
                                              "(\\(6 MONTHS - 4 YEARS\\))") |
                                     str_detect(IMMUNE_NAME,
                                                "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                                   "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)", 
                                   "Adult (12yo+)")),
           Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
                        ifelse(str_detect(IMMUNE_NAME, "MODERNA") |
                                 str_detect(
                                   IMMUNE_NAME,
                                   "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                               "Moderna",
                               ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
                                      NA))),
           Dose = ifelse(
             str_detect(replace_na(PRC_NAME, ""), "DOSE 1"), "Dose 1",
             ifelse(
               str_detect(replace_na(PRC_NAME, ""), "DOSE 2"), "Dose 2",
               ifelse(
                 str_detect(replace_na(PRC_NAME, ""), "(DOSE 3)|(BOOSTER)"),
                 "Dose 3/Booster",
                 ifelse(
                   str_detect(replace_na(RESPONSE_LIST, ""), "First Dose"),
                   "Dose 1",
                   ifelse(
                     str_detect(replace_na(RESPONSE_LIST, ""), "Second Dose"),
                     "Dose 2",
                     ifelse(
                       str_detect(replace_na(RESPONSE_LIST, ""),
                                  "(Third Dose) | (Booster Dose)"),
                       "Dose 3/Booster",
                       ifelse(VaxType %in% "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)",
                              "Dose 1", "Dose 3/Booster"))))))),
           Date = as.Date(str_extract(IMMUNE_DATE,
                                      "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
                          format = "%d-%b-%Y")
           ) %>%
    rename(Department = DEPARTMENT_NAME)

  weekly_admin_summary <- weekly_vax_admin %>%
    filter(!is.na(Department)) %>%
    group_by(Date, Department, `Setting Grouper`, 
             Site, `Hospital Roll Up`, 
             VaxType, Dose, Mfg) %>%  
    summarize(Count = n()) %>%
    ungroup()

  # Bind hybrid repository repository and most recent week's vaccine administration data
  hybrid_repo <- rbind(hybrid_repo, weekly_admin_summary)

  # Save new repository
  saveRDS(sched_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

} else {

@@

setting_kable(setting = "Hospital POD",
              vax_type = "Adult (12yo+)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (Pfizer 5-11yo)")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")

@@

setting_kable(setting = "MSHS Practice",
              vax_type = "Adult (12yo+)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (Pfizer 5-11yo)")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")

@@

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Adult (12yo+)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (Pfizer 5-11yo)")

setting_kable(setting = "MSHS Inpatient & ED",
              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")

@@

*   Immunizations with no associated Department/Epic ID excluded from analysis.
*   Vaccine type (Adult (12yo+), Peds (5-11yo), Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)) based on Immunization Name in Epic.
*   Vaccine dose based on the following logic:
    1. PRC_NAME field in Epic for clearly defined visits.
    2. RESPONSE_LIST field completed during vaccination noting the dose in the series for ambiguously defined visits (ie, well visits, follow ups, etc.)
    3. If both of these are empty, the dose is assumed to be Dose 1 for Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo) or Dose 3/Booster for Peds (5-11yo) and Adults (12+).
